---
title: "Weather Data Wrangling"
author: "Jeffrey Long"
date: "`r Sys.Date()`"
output:
      rmarkdown::html_vignette:
        fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Climate Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This program is a demo of data wrangling possibilities in R using
data from the nearest weather station to my home in Duboce Triangle, SF, CA.
The National Oceanic and Atmospheric Administration (NOAA)
National Centers For Environmental Information,
https://www.ncdc.noaa.gov/cdo-web/datatools allowed local station data
to be ordered and downloaded.

The first datasets obtained for station USW00023272 were daily summaries and hourly precipitation for all time.

```{r}
library(tidyverse)
```

## Data

Loading SF Weather data from September 2017 to earliest record.

```{r message=FALSE}
library(readr)
sfDaily <- read_csv("../data/sf1921to2017GhcnDaily.csv")
# Checking if any columns have just NAs. None do. So none are removed.
sfDaily <- sfDaily[,colSums(is.na(sfDaily))<nrow(sfDaily)]
```

## San Francisco Yearly Average Max Temp

```{r, fig.cap = "Duboce Triangle, SF, CA"}
# fig.show='hold' ## for side by side plots
sfDaily$YEAR <- substring(sfDaily$DATE,1,4)
#newDf <- df %>%
#  group_by(groupVar) %>%
#  summarize(df = mean(result))
sfYearMax <- sfDaily %>%
  group_by(sfDaily$YEAR) %>%
  summarise((sfDaily = mean(TMAX)))
plot(sfYearMax, pin = 6,6)
```


## Recent Data

 The average $Max = \sum DailyTemp_{Max} / N days$, footnote^[some reference to see].

```{r, echo=FALSE, results='asis'}
knitr::kable(tail(sfYearMax, 17))
```

> [Me](http://jeffreycarllong.com/)
